Towards One-Step, Three-Factor \\ Authentication with EarEEG

### 2017-09-19 paper.tex
2 line title
Nick and John updates

\title{Towards One-Step, Three-Factor Authentication with EarEEG}

@@

\begin{abstract}
Multifactor authentication presents a robust method to secure our private information, but typically requires multiple actions by the user resulting in a high cost to usability and limiting adoption. A usable system should also be unobtrusive and inconspicuous. We present a system that can provide all three factors of authentication (knowledge, possession, and inherence) in a single step via an earpiece which implements brain-based authentication using in-ear electroencephalography (EEG). We demonstrate its potential by collecting EEG data using manufactured custom-fit earpieces with embedded electrodes. Across all participants’ best-performing “passthoughts”, we are able to achieve 0\% false acceptance and 0.36\% false rejection rates using one earpiece with three electrodes. Furthermore, we find no successful attempts simulating impersonation attacks. We also report perspectives from our participants and discuss directions for future work. Our results indicate that a single electrode-laden earpiece could provide a discreet, convenient, and robust method for one-step, three-factor authentication.

@@

The concept of in-ear EEG was introduced in 2011 with a demonstration of the feasibility of recording brainwave signals from within the ear canal \cite{Looney2011}. The in-ear placement can produce signal-to-noise ratios comparable to those from conventional EEG electrode placements, is robust to common sources of artifacts, and can be used in a brain-computer interface (BCI) system based on auditory and visual evoked potentials \cite{Kidmose2013a}. An 80\% accuracy level was achieved for user authentication using in-ear EEG captured with a modified single-channel consumer-grade device \cite{curran2016passthoughts}. Our study markedly improves on these results by incorporating a physical token (a possession factor) in the form of custom-fitted earpieces with three electrodes each vs. the single channel used in previous work. Additionally we use the OpenBCI system which allows us to capture raw data (the device used in previous work used an unknown proprietary algorithm), simultaneously record from the scalp for validation, and report impedance measures important to data quality assessment and authentication.

@@

Seven male, right-handed participants (P1-P7), 5 students and 2 non-students, completed our study protocol approved by our local ethics review board. Though this sample is relatively homogenous and greater diversity is necessary for a larger real-world feasibility assessment, this quality interestingly functions to strengthen the results of this initial exploration (see details in Discussion). After participants' 3D ear molds were obtained and their fit and electrical impedance was checked, the collection of data for authentication analyses commenced. Data collection consisted of participants completing a demographics questionnaire, a set up period with the OpenBCI system and earpieces with a second impedance check, their performance of 9 mental tasks, and finally a post-experiment questionnaire.

@@

To produce custom ear impressions we first cleaned subjects' ears and injected silicon into the ear canals. A cotton ball with a string attached was placed into the ear canal first. When the silicon dried after a few minutes, the string was pulled to remove the impression from the ear canal. This impression was then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels were created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3D model was then sent to a 3D printer after which wires, leads, and associated AgCl electrodes were installed. The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}. We reduced the number of canal electrodes in order to prevent electrical bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal). We also reduced the number of electrodes in the concha to one. An example of one of the manufactured earpieces is shown in Figure \ref{fig:earpiece_diagram}.

@@

We used a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants. \cite{Chuang2013b, curran2016passthoughts} Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli. The 9 authentication tasks and their attributes are listed in Table \ref{tab:tasks}. Our strategy was to select tasks that captured a diversity across dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known effects on EEG), and different types of mental imagery.

@@

\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret}? & \textbf{Eyes} & \textbf{Imagery}\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Imagine attempting a chosen physical activity & No & Yes & Closed & Motor\\
Song & Imagine hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagine a chosen spoken phrase & No & Yes & Closed & Aural\\
Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a chosen person's face & No & Yes & Closed & Visual\\
Sequence & Imagine a chosen face, number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

\subsection{Data Collection Protocol}
%\label{sec:org2041857}
All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode. For EEG recording we used an 8-channel OpenBCI system \cite{michalska2009openbci} which is open-source and costs about 600 USD; an alternative to medical-grade EEG systems (\textgreater20,000 USD), with demonstrated effectiveness \cite{Frey2016}. The ground was placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and reference on the left mastoid. The AFz ground location was intentional to not bias left or right ear recordings, though future systems using one ear only should test relocating the ground to a site on one ear (e.g. the earlobe). 6 channels were used for the 3 electrodes on each earpiece (shown in Figure \ref{fig:earpiece_diagram}); for the remaining 2 channels one AgCl ring electrode was placed on the right mastoid for later re-referencing, and one at approximately Fp1 (ISEP location above the left eye) to validate the data collected in the ears against a common scalp-based placement. Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface. Audio stimuli were delivered through small tubes in the earpieces.

@@

Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \cite{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \cite{Chen2016}, to analyze the mental task EEG data. Compared to other linear classifiers, XGBoost uses gradient boosting in which an algorithm generates an ensemble (in this case, a decision tree) of weak linear classifiers that minimizes a given loss function. Gradient boosting gives better results in linear classification problems without manually tuning hyperparameters. XGBoost atuomatically optimized using the "error" hyperparameter, XGBoost's binary classification error rate calculated as N(wrong cases)/N(all cases). For the predictions, the evaluation regards the instances with prediction value larger than 0.5 as positive instances, and the others as negative instances.

To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed a fourier transform to produce power spectra for each electrode during that slice. We concatenated all electrode power spectra together, and XGBoost performed its own principal component analysis on all concatenated vectors. For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task.

We trained the classifier such that positive examples were from the target participant and target task, and negative examples were randomly selected tasks from any other participant. From this corpus of positive and negative samples, we withheld one third of data for testing. The remaining training set was fed into a XGBoost's cross-validation (CV) method, which we set to iteratively tweak parameters over a maximum of fifty rounds of CV to minimize loss. After CV, the updated classifier (with parameters applied) predicted labels on each sample in the test set, and we calculated FAR and FRR from its results. To further test the robustness of the system, we also conducted a "leave one out" process for the best performing tasks in which each participant's FAR was calculated once leaving out every other participant (e.g. CV for P1 with P2 left out, then CV for P1 with P3 left out, etc. for every participant combination).

\section{Results}
%\label{sec:org6705b1d}
\subsection{Combinations of electrodes}
%\label{sec:org21b14ae}

@@

Our results indicate acceptable accuracy using data from the left ear alone. This corresponds to our desired scenario, in which the device could be worn like an earbud. As such, we focus on results from only the left ear in remaining analyses.

@@

In the previous section, we trained and tested a passthoughts classifier with each task as the passthought, for all participants. Our analyses revealed the left ear alone produced suitable results, and thus wearing two earpieces is likely unecessary. Using only data from the left ear electrodes, the performance of each task for each participant is shown in Tables \ref{tab:farall} and \ref{tab:frrall}. For each participant we find at least one task that achieves 0\% FAR and for all but two participants a task where both the FAR and FRR are 0\%.

@@

All best-performing tasks in our best-case set achieved perfect FARs and only two participants had a best test with an FRR greater than zero. Each task achieved perfect 0 FAR and FRR for at least one participant, notably \textit{breathe} and \textit{song - open} achieved perfect FAR and FRR for 3 out of 7 participants. Interestingly, tasks like \textit{breathe} and \textit{breathe - open} performed very well despite lacking a personalized secret, indicating that even when the task may be the same across participants our classifier was still able to distinguish between them.

@@

These results establish good performance in our default training strategy, in which we count as negative examples recordings from the wrong participant performing any task. For comparison, we report three other analyses with differing negative examples: the correct task recorded from the wrong participant (inherence only), the wrong task recorded from the correct participant (knowledge only), and a combination of these two. Positive examples were always correct participant, correct task.

@@

Finally, our "leave one out" analysis on the best tasks maintained 0 FAR across all participant combinations.

@@

A subset of participants completed a usability questionnaire. This questionnaire asked them to rate each mental task on four 7-point likert-type scales: ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting. The \textit{breathe} and \textit{listen} tasks were rated easiest to use (\(\mu\)=6.75), \textit{Sequence}, \textit{song}, and \textit{song - open} as most engaging (\(\mu\)=5), \textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) as most repeatable. For likeliness to use for authentication, \textit{song - open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly. Participants also ranked the tasks overall from most (1) to least (9) favorite. \textit{Song - open} ranked most favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75). \textit{Sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were ranked least favorite.

@@

Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers. We find zero successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}). However, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., \textit{breathe}). In fact, in all 1,800 spoof attempts (200 attempts for each of the 9 classifiers), we do not find a single successful attack on any of P6's classifiers.

@@

Our findings demonstrate the apparent feasibility of a passthoughts system consisting of a single earpiece with three electrodes and a reference, all in or on the left ear. FARs and FRRs are very low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information. Participants' best-performing tasks or passthoughts typically see virtually no errors in our training. Passthoughts also appear to be quite memorable given our two week recall follow-up and some were rated highly repeatable and engaging. Furthermore, no spoofed attacks were successful in our cursory analyses. These results are a marked improvement upon the only other in-ear EEG passthoughts work we are aware of \cite{curran2016passthoughts}, from 80\% accuracy to 99.82\%. This improvement is likely due to the custom-fit quality of the earpieces, the use of 3 electrodes in the ear as opposed to 1, and possibly the XGBoost classifier instead of a generic support vector machine.

>>>>

\title{Towards One-Step, Three-Factor \\ Authentication with EarEEG}

@@

\begin{abstract}
Multifactor authentication presents a robust method to secure our private information, but typically requires multiple actions by the user resulting in a high cost to usability and limiting adoption. A usable system should also be unobtrusive and inconspicuous. We present a system that can provide all three factors of authentication (knowledge, possession, and inherence) in a single step via an earpiece which implements brain-based authentication using in-ear electroencephalography (EEG). We demonstrate its potential by collecting EEG data using manufactured custom-fit earpieces with embedded electrodes. Across all participants’ best-performing “passthoughts”, we are able to achieve 0\% false acceptance and 0.36\% false rejection rates, an overall accuracy of 99.82\%, using one earpiece with three electrodes. Furthermore, we find no successful attempts simulating impersonation attacks. We also report perspectives from our participants and discuss directions for future work. Our results indicate that a single electrode-laden earpiece could provide a discreet, convenient, and robust method for one-step, three-factor authentication.

@@

The concept of in-ear EEG was introduced in 2011 with a demonstration of the feasibility of recording brainwave signals from within the ear canal \cite{Looney2011}. The in-ear placement can produce signal-to-noise ratios comparable to those from conventional EEG electrode placements, is robust to common sources of artifacts, and can be used in a brain-computer interface (BCI) system based on auditory and visual evoked potentials \cite{Kidmose2013a}. One study attempted to demonstrate user authentication using in-ear EEG, but was only able to attain an accuracy level of 80\%, limited by their use of a consumer-grade device with a single-electrode generic fit earpiece \cite{curran2016passthoughts}. Our study improves on these results by incorporating a physical token (a possession factor) in the form of custom-fitted earpieces with three electrodes each vs. the single channel used in previous work. Additionally we use the OpenBCI system which allows us to capture raw data (the device used in previous work used an unknown proprietary algorithm), simultaneously record from the scalp for validation, and report impedance measures important to data quality assessment and authentication.

@@

Seven male, right-handed participants (P1-P7), five students and two non-students, completed our study protocol approved by our local ethics review board. Though this sample is relatively homogenous and greater diversity is necessary for a larger real-world feasibility assessment, this quality interestingly functions to strengthen the results of this initial exploration (see details in Discussion). After participants' 3D ear molds were obtained and their fit and electrical impedances were checked, the collection of data for authentication analyses commenced. Data collection consisted of participants completing a demographics questionnaire, a set up period with the OpenBCI system and earpieces with a second impedance check, their performance of nine mental tasks, and finally a post-experiment questionnaire.

@@

To produce custom ear impressions we first cleaned subjects' ears and injected silicon into the ear canals. A cotton ball with a string attached was placed into the ear canal first. When the silicon dried after a few minutes, the string was pulled to remove the impression from the ear canal. This impression was then scanned with a 3D scanner and the resulting scan modified based on some heuristics to achieve a comfortable fit and to ensure the intended electrode sites will make good contact with the skin. Channels were created in the 3D model to allow wire leads and associated EEG electrodes as well as a plastic tube to deliver audio. This 3D model was then sent to a 3D printer after which wires, leads, and associated AgCl electrodes were installed. The positions of the earpiece electrodes were simplified from those described in \cite{Mikkelsen2015}. We reduced the number of canal electrodes in order to prevent electrical bridging and positioned them approximately 180 degrees apart in the canal (posterior/back and anterior/front locations in the canal). One other electrode was placed in the concha. An example of one of the manufactured earpieces is shown in Figure \ref{fig:earpiece_diagram}.

@@

We used a set of mental tasks based on findings in related work regarding the relative strengths of different tasks in authentication accuracy and usability as reported by participants. \cite{Chuang2013b, curran2016passthoughts} Furthermore, given the in-ear placement of the electrodes and therefore the proximity to the temporal lobes containing the auditory cortex, we tested several novel authentication tasks based specifically on aural imagery or stimuli. The nine authentication tasks and their attributes are listed in Table \ref{tab:tasks}. Our strategy was to select tasks that captured a diversity across dimensions of external stimuli, involving a personal secret, eyes open or closed (due to known effects on EEG), and different types of mental imagery.

@@

\textbf{Task} & \textbf{Description} & \textbf{Stimuli}? & \textbf{Secret}? & \textbf{Eyes} & \textbf{Imagery}\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Imagine attempting a chosen physical activity & No & Yes & Closed & Motor\\
Song & Imagine hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagine a chosen spoken phrase & No & Yes & Closed & Aural\\
Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a chosen person's face & No & Yes & Closed & Visual\\
Sequence & Imagine a chosen face, number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{Authentication tasks and their properties. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

\subsection{Data Collection Protocol}
%\label{sec:org2041857}
All sites were cleaned with ethanol prior to electrode placement and a small amount of conductive gel was used on each electrode. For EEG recording we used an 8-channel OpenBCI system \cite{michalska2009openbci} which is open-source and costs about 600 USD; an alternative to medical-grade EEG systems (\textgreater20,000 USD), with demonstrated effectiveness \cite{Frey2016}. The ground was placed at the center of the forehead, approximately AFz according to the 10-20 International Standard for Electrode Placement (ISEP), and reference on the left mastoid. The AFz ground location was intentional to not bias left or right ear recordings, though future systems using one ear only should test relocating the ground to a site on one ear (e.g. the earlobe). six channels were used for the three electrodes on each earpiece (shown in Figure \ref{fig:earpiece_diagram}); for the remaining two channels one AgCl ring electrode was placed on the right mastoid for later re-referencing, and one at approximately Fp1 (ISEP location above the left eye) to validate the data collected in the ears against a common scalp-based placement. Before beginning the experiment, the data from each channel was visually inspected using the OpenBCI interface. Audio stimuli were delivered through small tubes in the earpieces.

@@

Since past work has shown that classification tasks in EEG-based brain-computer interfaces (BCI) are linear \ref{Garrett2003a}, we used XGBoost, a popular tool for logistic linear classification \ref{Chen2016}, to analyze the mental task EEG data. Compared to other linear classifiers, XGBoost uses gradient boosting in which an algorithm generates aa decision tree of weak linear classifiers that minimizes a given loss function. Gradient boosting generally improves linear classification results without manually tuning hyperparameters.

To produce feature vectors, we took slices of 100 raw values from each electrode (about 500ms of data), and performed a fourier transform to produce power spectra for each electrode during that slice. We concatenated all electrode power spectra together. No dimensionality reduction was applied. For each task, for each participant, 100 seconds of data were collected in total across 10 trials of 10 seconds each, resulting in 200 samples per participant, per task.

We trained the classifier such that positive examples were from the target participant and target task, and negative examples were randomly selected tasks from any other participant. From this corpus of positive and negative samples, we withheld one third of data for validation. The remaining trainset was used to cross-validate an algorithm over 100 rounds on different splits of the data. The results of each cross-validation (CV) steps were used to iteratively tweak classifier parameters.

For the predictions, the evaluation regards the instances with prediction value larger than 0.5 as positive instances, and the others as negative instances. After updating classifier parameters, the classifier was tested on the withheld validation set. Since negative examples far outweigh positive examples in this dataset, XGBoost atuomatically optimized using the ”error” hyperparameter. Over a set of \(E\) examples containing \(E_W\) wrong examples \(E_W\subset{E}\), XGBoost’s binary classification error rate \(\epsilon\) is calculated as

\[ \epsilon = E_W / E \]

We calculated FAR and FRR from these results. Over false attempts \(FA\) of which some subset \(FA_S\) were successful, and true attempts \(TA\) over which some subset \(TA_U\) were unsuccessful:

\[ FAR = FA_S / FA \]
\[ FRR = TA_U / TA \]

To further test the robustness of the system, we also conducted a ”leave one out” process for the best performing tasks in which each participant’s FAR was calculated once leaving out every other participant (e.g. CV for P1 with P2 left out, then CV for P1 with P3 left out, etc. for every participant combination).

\section{Results}
%\label{sec:org6705b1d}
\subsection{Electrode Configuration}
%\label{sec:org21b14ae}

@@

Our results indicate acceptable accuracy using data from the left ear alone. This corresponds to a desirable scenario, in which the device could be worn like an single earbud. As such, we focus on results from only the left ear in remaining analyses.

@@

Using only data from the left ear electrodes, the FARs and FRRs of each task for each participant are shown in Tables \ref{tab:farall} and \ref{tab:frrall}, respectively. We find at least one task for each participant that achieves 0\% FAR, and for five participants a task where both the FAR and FRR are 0\%. Each task achieved perfect 0 FAR and FRR for at least one participant, notably \textit{breathe} and \textit{song - open} achieved perfect FAR and FRR for three out of seven participants.

@@

FAR and FRR results by task are shown in Figure \ref{fig:meanByTask}, averaged across participants. Across all tasks, the sport task produced the lowest FAR. Specifically, it produced 0.0\% FAR for all seven participants, with a corresponding 1.8\% FRR. This suggests that the authentication scheme can work very well even if we limit the passthoughts to just a single task category, where the users could choose a personalized secret for that task.Interestingly, tasks like \textit{breathe} and \textit{breathe - open} performed very well despite lacking a personalized secret, indicating that even when the task may be the same across participants our classifier was still able to distinguish between them.

As an omnibus metric, the half total error rate (HTER) is defined as the average of the FAR and FRR:

\[ HTER = (FAR + FRR) / 2 \]

and from this we estimate authentication accuracy, $ACC$, as:

\[ ACC = 100*(1-HTER) \]

Using our best performing tasks' FARs, averaging 0\% and these tasks' associated FRRs, averaging 0.36\%, we estimate a best-case authentication accuracy of 99.82\%.

@@

These results thus far establish good performance in our default training strategy, in which we count as negative examples recordings from the wrong participant performing any task. For comparison, we report three other analyses with differing negative examples: the correct task recorded from the wrong participant (inherence only), the wrong task recorded from the correct participant (knowledge only), and a combination of these two. Positive examples were always the correct participant performing the correct task.

@@

Finally, our "leave one out" analysis with participants' best tasks maintained 0 FAR across all participant combinations.

@@

Before the end of othe session, participants completed a usability questionnaire. This questionnaire asked them to rate each mental task on four 7-point likert-type scales: ease of use, level of engagement, perceived repeatability, and likeliness to use in a real-world authentication setting. The \textit{breathe} and \textit{listen} tasks were rated easiest to use (\(\mu\)=6.75), \textit{Sequence}, \textit{song}, and \textit{song - open} as most engaging (\(\mu\)=5), \textit{Breathe} (\(\mu\)=7) and \textit{listen} (\(\mu\)=6.75) as most repeatable. For likeliness to use for authentication, \textit{song - open} (\(\mu\)=5) and \textit{sequence} (\(\mu\)=4.25) were rated highest, though modestly. Participants also ranked the tasks overall from most (1) to least (9) favorite. \textit{Song - open} ranked most favorites (\(\mu\)=4.25) followed by a tie between \textit{breathe - open}, \textit{song}, and \textit{speech} (\(\mu\)=4.75). \textit{Sequence} (\(\mu\)=7.75) and \textit{face} (\(\mu\)=6.75) were ranked least favorite.

@@

Since every participant has one classifier per task (for which that task is the passthought), we are able to make 200 spoofed attempts with the correct passthought on each of P6's classifiers. We find zero successful spoof attempts for tasks with a chosen secret (e.g., \textit{song} or \textit{face}). In addition, we also do not find any successful spoof attacks for tasks with no chosen secret (e.g., \textit{breathe}). In fact, in all 1,800 spoof attempts (200 attempts for each of the nine classifiers), we do not find a single successful attack on any of P6's classifiers.

@@

Our findings demonstrate the apparent feasibility of a passthoughts system consisting of a single earpiece with three electrodes and a reference, all in or on the left ear. FARs and FRRs are very low across all participants and tasks, with FARs overall lower than FRRs, a desirable pattern in terms of authenticating access to potentially sensitive information. Participants' best-performing tasks or passthoughts typically see virtually no errors in our training. Passthoughts also appear to be quite memorable given our two week recall follow-up and some were rated highly repeatable and engaging. Furthermore, no spoofed attacks were successful in our cursory analyses. These results are a marked improvement upon the only other in-ear EEG passthoughts work we are aware of \cite{curran2016passthoughts}, from 80\% accuracy to 99.82\%. This improvement is likely due to the custom-fit quality of the earpieces, the use of three electrodes in the ear as opposed to one, and possibly the XGBoost classifier instead of a generic support vector machine.
